\documentclass[12pt]{article}
\usepackage{lipsum}
\linespread{1.5} 
\usepackage[utf8]{inputenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx,epstopdf,subfigure,mathtools,mathrsfs} 
\usepackage[normalem]{ulem}
\PassOptionsToPackage{usenames,dvipsnames}{xcolor}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\cmt}[1]{\color{blue}#1\normalcolor}
% Path for Figures
\graphicspath{{../}}

% VECTOR AND MATRIX NOTATION
\newcommand{\V}[1]{\boldsymbol{#1}}                 % vector notation
\newcommand{\M}[1]{\boldsymbol{#1}}
\newcommand{\Lop}[1]{\mathcal{#1}}
\newcommand{\bm}[1]{\boldsymbol{#1}}
\newcommand{\ind}[2]{{#1}_{#2}}
\newcommand{\ddt}[1]{\frac{\partial #1}{\partial t}}


\global\long\def\D#1{\Delta#1} 
\global\long\def\d#1{\delta#1} 

\global\long\def\norm#1{\left\Vert #1\right\Vert }
\global\long\def\abs#1{\left|#1\right|}
\global\long\def\bm#1{\V#1}
\global\long\def\eqd{:=}

\global\long\def\grad{\M{\nabla}}
%\global\long\def\av#1{\left\langle #1\right\rangle }

% NOTATION SPECIFIC TO THIS PAPER
\global\long\def\intmat{\mathcal{D}^{-1}}
\global\long\def\Slet#1{S\left(#1\right)}
\global\long\def\Dlet#1{D\left(#1\right)}
\global\long\def\Knel#1{K\left(#1\right)}
\global\long\def\Xs{\V{X}_s}
\global\long\def\EPMI{\frac{1}{8\pi\mu}}
\global\long\def\ML{ \M{M}^\text{L}}
\global\long\def\MFP{\Lop{M}^\text{FP}}
\global\long\def\MJF{\Lop{M}^\text{JF}}
\global\long\def\aRPY{a^*}%\displaystyle{\epsilon L \sqrt{\frac{3}{2}}}}

\global\long\def\eqd{:=}

\usepackage{hyperref}
\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}

% Set the margins for 1" around
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.1in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textwidth}{6.4in}
\setlength{\textheight}{8.9in}

\title{An integral-based spectral method for slender body hydrodynamics}
\author{Ondrej Maxian and Aleksandar Donev}

\begin{document}

\maketitle

\abstract{\cmt{To be added later.}%Actin filaments, microtubules, and other inextensible filaments play a vital role in the cell division process. The multiscale nature of these objects (aspect ratios as large as 10,000) makes their numerical simulation challenging. We describe a new method for rapidly computing the dynamic behavior of inextensible slender biological filaments in Stokes flow. Our approach is based on using an integral equation to restrict the velocity obtained from slender body theory to the space of inextensible motions. By using a spectral discretization of the local and nonlocal slender body theory operators and a second-order temporal discretization, we achieve improved robustness and accuracy, both of which are demonstrated here through numerical examples. We conclude by applying our method to a cross-linked actin mesh. 
}

\section{Introduction}
\input{Paper_Intro.tex}

\section{Slender body theory}
\input{Paper_SlenderBodyReview.tex}

\section{Inextensible filaments}
In this paper, we consider inextensible filaments which can bend. Twist elasticity is neglected, as it has been in previous work on biological filaments \cite{ehssan17}. At each instant in time, fibers resist bending with bending force density (per unit length) $\V{f}^E\left(\V{X}\right)$. Inextensibility can be enforced by introducing Langrange multiplier force densities $\V{\lambda}\left(\V{X}\right)$. Thus the PDE that we need to solve is given by (dropping the explicit dependence on $s$), 
\begin{equation}
\label{eq:fibPDE}
\frac{\partial \V{X}}{\partial t} - \V{U}_0(\V{X}) = \Lop{M}\left[\V{X}\right] \left(\V{f}^E\left(\V{X}\right)+\V{\lambda}\left(\V{X}\right)\right),
\end{equation}
where the mobility operator $\Lop{M}$ is defined in Eq.\ \eqref{eq:fibevcont}. The fibers are assumed to be free, and are therefore subject to the boundary conditions \cite{ts04}
\begin{equation}
\label{eq:frBCs}
\V{X}_{ss}\left(s=0,L\right)=\V{X}_{sss}\left(s=0,L\right)=\bm{0}.
\end{equation}
Here by $\V{X}_{ss}$ we mean $\left(\ind{\V{X}}{i}\right)_{ss}$ for all fibers $i$ (and similarly for any number of $s$ derivatives). 

The fibers are also constrained to be inextensible, so that 
\begin{equation}
\label{eq:inex}
\V{X}_s(s,t) \cdot \V{X}_s(s,t)=1 
\end{equation}
for all times $t$. In summary, we solve Eq.\ \eqref{eq:fibPDE} subject to boundary conditions in Eq.\ \eqref{eq:frBCs} and constraints in Eq.\ \eqref{eq:inex}. We need to specify additional conditions to make the solution unique, as we discuss next. 

\input{Paper_InexTheory.tex}

\section{Numerical Methods}
This section is devoted to our spatial and temporal discretizations of Eq.\ \eqref{eq:saddleL2} (solving for $\V{\alpha}$) and Eq.\ \eqref{eq:defk} (updating the fiber tangent vector and position once $\V{\alpha}$ is known). We begin by laying out our spectral choice of basis functions $\phi_k$ and spectral spatial discretization in Section \ref{sec:discspat}. In Section \ref{sec:tint}, we discuss how our second-order temporal discretization avoids having to perform nonlinear solves and requires only a single evaluation of the nonlocal hydrodynamics for each timestep. We conclude this section by discussing how we actually evaluate each of the nonlocal terms to 3 digits of accuracy. 

\subsection{Spectral discretization \label{sec:discspat}}
\input{Paper_DiscrWk.tex}

\subsection{Temporal discretization \label{sec:tint}}
\input{Paper_Temporal.tex}

\subsection{Efficient evaluation of nonlocal SBT}
The evaluation of the $\M{M}_{NL}$ term in Eq.\ \eqref{eq:CNnLUs} can be broken down into three parts. First, we must evaluate the singular finite part integral in Eq.\ \eqref{eq:fibevcont}. Second, we must be able to evaluate the Stokeslet and Doublet kernels on other fibers with controlled accuracy, independent of how close together the fibers are. And finally, in order to efficiently simulate systems with $\mathcal{O}(100-1000)$ fibers, we must be able to efficiently sum the kernels over many fibers. These sums are quadratic in the number of fibers when done naively. 

\subsubsection{Finite part integral \label{sec:tornFP}}
\input{Paper_TornFP.tex}

\subsection{Near-singular integrals \label{sec:specquad}}
\input{Paper_SpecialQuad.tex}


\subsection{Fast summation \label{sec:ewald}}
\input{Paper_Ewald.tex}


\subsection{Implementation}
We use a Python implementation. \cmt{More to come here as (a) we discuss what to put here and (b) the code is finalized}. 

\section{Numerical tests}
In this section, we present two numerical tests that demonstrate the improved accuracy and robustness of our algorithm. In Section \ref{sec:local}, we first consider a single relaxing fiber in free space. We directly compare our results using local drag to those of \cite{ehssan17} to demonstrate the improved spatial discretization of inextensibility and boundary conditions. We also show second-order temporal accuracy, which improves on the first-order scheme used in \cite{ehssan17}. Next, in Section \ref{sec:fallfibs}, we consider falling fibers in periodic boundary conditions and show that we maintain second-order accuracy in time even when non-local terms are included. 

\subsection{Single fiber with local drag \label{sec:local}}
\input{Paper_LocalTest.tex}

\subsection{Falling fibers in a periodic domain \label{sec:fallfibs}}


\section{Application: cross-linked actin mesh}
\subsection{Cross-linking forces}
\subsection{Results}

\section{Conclusion}

\appendix

\section{Near fiber quadrature \label{sec:nearfibtests}}
\input{Paper_SpecQAppen.tex}


\bibliographystyle{plain}

\bibliography{SlenderBib}

\end{document}
